Super-resolution of Aeromagnetic Survey Data

### 2023-10-12 discussion.tex
Write concluding remarks

We identify opportunities in \Cref{ch:futurework} for future work stemming from our contribution  of enhancing potential field methods in geophysics.

>>>>

\Cref{ch:futurework} discussed future work arising from the contributions of this thesis for enhancing potential field methods in geophysics, with a focus on possible approaches to characterise and improve the confidence in the use of  these methods by the geophysics community.
In summary, this thesis explored how advances in deep learning may be adapted and extended to enhance the processing of potential field geophysical data.
The presented approaches, results, and considerations have established the capacity for these contemporary methods in deep learning to overcome current challenges in geoscience.
